Symbolic Weighted Language Models and\\ Quantitative Parsing over Infinite Alphabets

### 2021-07-16 main.tex
example VPA: measure

% comments in margin with \todo command
\usepackage[colorinlistoftodos]{todonotes} % option disable to hide todos
% command todo : options
% - noline: no line connecting the note with the place in the text where the note occurs in the latex code
% - fancyline : curved arrow from note to inssertion point
% - inline: place a todonote inside the text instead of in the margin
% - author=name
\newcommand{\florent}[1]{\todo[noline,size=\tiny,color=yellow!40]{#1}}
\newcommand{\lydia}[1]{\todo[noline,size=\tiny,color=red!30]{#1}}
\newcommand{\philippe}[1]{\todo[noline,size=\tiny,color=green!30]{#1}}

@@

Let us assume a third component in the symbols of $\Deltac$ 
which is the duration of the associated time interval.
It is used to check the timestamps in the symbols.
%
For instance, the following call transition starts in state
$q_{{i}/{c}}$, meaning that the current interval is number~$i$ 
amongst $c$ sub-intervals of duration~$\ell$ (as indicated by the stack top).
It reads a new time-division symbol~$\ccall{d}$.
The date for this symbol has to be the time $\tau$ 
for the previous time-division symbol read~$\ccall{c}$ (found on the stack)
plus the total duration of intervals read so far, $i \ell$.
The new current interval duration is~$\frac{\ell}{d}$.

\(
\weic\bigl(q_{{i}/{c}}, 
           [\ccall{c}\ts{\tau}\ts{\ell}], q, 
           [\ccall{d}\ts{\tau + i\ell}\ts{\frac{\ell}{d}}], q_{{i+1}/{c}},
           q_{{0}/{d}} \bigr) = \alpha_d
\).

@@

\noindent
Reading an event is done with:
\(
\weii\bigl(q_{{i}/{d}}, 
           [\ccall{d}\ts{\tau}\ts{\ell}], q_{{j}/{c}}, 
           [\mu\ts{\tau + i\ell}], q_{{i+1}/{d}} \bigr) = \alpha_\mu
\).
% cas des barres de mesure?
\endex
\end{example}

>>>>

% comments in margin with \todo command
\usepackage[colorinlistoftodos]{todonotes} % option disable to hide todos
% command todo : options
% - noline: no line connecting the note with the place in the text 
%   where the note occurs in the latex code
% - fancyline : curved arrow from note to inssertion point
% - inline: place a todonote inside the text instead of in the margin
% - author=name
\newcommand{\florent}[1]{\todo[noline,size=\tiny,color=yellow!40]{#1}}
\newcommand{\lydia}[1]{\todo[noline,size=\tiny,color=red!30]{#1}}
\newcommand{\philippe}[1]{\todo[noline,size=\tiny,color=green!30]{#1}}

@@

Let us assume a third component in the symbols of $\Deltac$ 
which is the duration of the associated time interval.
It is used to check the timestamps in the symbols.
%
For instance, the following call transition starts in state
$q_{{i}/{c}}$, meaning that the current interval has number~$i$ 
amongst $c$ sub-intervals of duration~$\ell$ (as indicated by the stack top).
It reads a new time-division symbol~$\ccall{d}$.
The date for this symbol has to be the time $\tau$ 
for the previous time-division symbol read~$\ccall{c}$ (found on the stack)
plus the total duration of intervals read so far, $i \ell$.
The new current interval duration is~$\frac{\ell}{d}$.
%
\(
\weic\bigl(q_{{i}/{c}}, 
           \ccall{c}\ts{\tau}\ts{\ell}, q, 
           \ccall{d}\ts{\tau + i\ell}\ts{\frac{\ell}{d}}, q_{{i+1}/{c}},
           q_{{0}/{d}} \bigr) = \alpha_d
\).

@@

\noindent
Reading an event is done with:
\(
\weii\bigl(q_{{i}/{d}}, 
           [\ccall{d}\ts{\tau}\ts{\ell}], q_{{j}/{c}}, 
           [\mu\ts{\tau + i\ell}], q_{{i+1}/{d}} \bigr) = \alpha_\mu
\).
% cas des barres de mesure?
** case of new measure symbol: $q_0$ is a special (initial) state.
first measure:
\(
\weiec\bigl(q_0, 
           \ccall{\mathsf{m}}\ts{0}\ts{1}, q_0, 
           q_0 \bigr) = \alpha_d
\).
new measure:
\(
\weic\bigl(q_{{c}/{c}}, 
           \ccall{\mathsf{m}}\ts{\tau}\ts{1}, q_0, 
           \ccall{\mathsf{m}}\ts{\tau + 1}\ts{1}, q_0,
           q_0 \bigr) = \alpha_d
\).
\endex
\end{example}
